A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-02-04 journal/abstract.tex
more small fixes

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a metric for measuring distance between executions, and specializes it to an important application: determining similarity of failing test cases for the purpose of automated fault identification and localization in debugging based on automatically generated compiler tests.  The metric is based on a causal concept of distance where executions are similar to the degree that changes in the program itself, introduced by mutation, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases for a compiler can be made to pass by applying the same mutant, those two tests are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,800 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.  We additionally show that this approach, though devised for compilers, is applicable as a conservative fault localization algorithm for other types of programs.

>>>>

Measuring the distance between two program executions is a fundamental problem in dynamic analysis of software, and useful in many test generation and debugging algorithms.  This paper proposes a metric for measuring distance between executions, and specializes it to an important application: determining similarity of failing test cases for the purpose of automated fault identification and localization in debugging based on automatically generated compiler tests.  The metric is based on a causal concept of distance where executions are similar to the degree that changes in the program itself, introduced by mutation, cause similar changes in the correctness of the executions.  Specifically, if two failing test cases for a compiler can be made to pass by applying the same mutant, those two tests are more likely to be due to the same fault.  We evaluate our metric using more than 50 faults and 2,800 test cases for two widely-used real-world compilers, and demonstrate improvements over state-of-the-art methods for fault identification and localization.  A simple operator-selection approach to reducing the number of mutants can reduce the cost of our approach by more than 70\%, while producing a gain in fault identification accuracy.  We additionally show that our approach, though devised for compilers, is applicable as a conservative fault localization algorithm for other types of programs.

### 2019-02-04 journal/introduction.tex
done
more small fixes

The proposed techniques in this paper are motivated in large part by progress in automated testing.  Recent advances, some implemented in powerful tools \cite{csmith,jsfunfuzz,ISSTA12,LangFuzz,ZhendongPLDI,ZhendongOOPSLA}, have made it easier to find subtle faults in modern optimizing compilers.  Unfortunately, the blessing of many failing test cases can become a curse for a developer.  Simply discovering which test cases in a large set of failures represent distinct faults (or already known faults) is a very difficult problem \cite{PLDI13,Podgurski04}.  For simple crashes and assertion violations, bucketing failures is sometimes easy.  When a failure is detected by differential testing \cite{Differential}, where two compilers or optimization levels disagree, the problem is so hard that it may turn potential users away from automated test generation \cite{PLDI13}.  Even once a fault is identified, fixing the problem can be very difficult.  Due to complexity of intermediate representation, interaction of optimizations, subtle language semantics, and other issues, debugging compiler faults may often be harder than debugging faults in other kinds of software (this is probably not limited to compilers; debugging systems software in general is hard \cite{mickens}).
This paper proposes the use of mutants \cite{mutant} to assist debugging based on large sets of automatically generated test cases.  The underlying idea is that if two failures can be repaired in the same way, even if that repair only avoids the failure and does not truly fix it, they are likely due to the same fault. Repairs can also provide  information for understanding and debugging discovered faults. The approach suggests a plausible metric for comparing any two program executions, not just failing test cases.  Comparing executions has been a prominent concept in dynamic analysis throughout much of the last two decades \cite{NearNeighbor,Sumner2011} (e.g., Ball's early discussion of profile similarity \cite{BallConcept}).

>>>>

The proposed techniques in this paper are motivated in large part by progress in automated testing.  Recent advances, some implemented in powerful tools \cite{csmith,jsfunfuzz,ISSTA12,LangFuzz,ZhendongPLDI,ZhendongOOPSLA}, have made it easier to find subtle faults in modern optimizing compilers.  Unfortunately, the blessing of many failing test cases can become a curse for a developer.  Simply discovering which test cases in a large set of failures represent distinct faults (or already known faults) is a very difficult problem \cite{PLDI13,Podgurski04}.  For simple crashes and assertion violations, bucketing failures is sometimes easy.  When a failure is detected by differential testing \cite{Differential}, where two compilers or optimization levels disagree, the problem is so hard that it may turn potential users away from automated test generation \cite{PLDI13}.  Such \emph{wrong code} bugs do not produce a crash, only two compiled programs with different, incorrect (in at least one case) behavior.  Even once a fault is identified, fixing the problem can be very difficult.  Due to complexity of intermediate representation, interaction of optimizations, subtle language semantics, and other issues, debugging compiler faults may often be harder than debugging faults in other kinds of software (this is probably not limited to compilers; debugging systems software in general is hard \cite{mickens}).
This paper proposes the use of mutants \cite{mutant} to assist debugging based on large sets of automatically generated test cases.  The underlying idea is that if two failures can be repaired, by applying the same program mutant, \emph{even if the repair only avoids the failure and does not truly fix it}, the two failures are likely due to the same fault. Repairs can also provide  information for understanding and debugging discovered faults. The approach suggests a plausible metric for comparing any two program executions, not just failing test cases.  Comparing executions has been a prominent concept in dynamic analysis throughout much of the last two decades \cite{NearNeighbor,Sumner2011} (e.g., Ball's early discussion of profile similarity \cite{BallConcept}).
